---
title: "README"
author: "Jack Chen"
date: "9/24/2022"
output: rmarkdown::github_document
  
---

```{r}
library(dplyr)
library(nycflights13)
library(ggplot2)
summary(flights)
```
How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
filter(flights,is.na(dep_time))
```

# They are 8255 missing dep_time in the flight data frame. In the meantime, the dep_delay, arr_time, arr_delay, and air_time are also missing. These rows are missing because they never depart, so they will not be a departure delay time, arrive delay time, and have no air flight time.

currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flights<- mutate(flights,
  dep_time = (dep_time %/% 100 * 60 + dep_time %% 100) %% (24*60),
  sched_dep_time = (sched_dep_time %/% 100 * 60 + sched_dep_time %% 100) %% (24*60)
)
summary(flights)
```
# The trnasformation process is that the dep_time and sched_dep_time are convennient for people to look at for example 24:00 stands for midnight 12:00pm. 1305 stands for 13:05 minutes. The relationship between the first two digits are multiples of hundreds. You need to divide the hundreds and you will only get the hour range between 1 and 24. Next you need to multiple the hour by 60 because you want the format to be in minutes. The last two digits are the minutes. This %% will give you the remainder only. You sum the hour in minutes and the remainder you will have the total time. In addition, they are 1440 minutes in a day. So you treat 1440 as 0 for a new day. 


Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

```{r}
flights %>%
  group_by(year,month,day) %>%
  summarise(canceled_per_day= sum(is.na(air_time)),
    mean_arr_delay = mean(arr_delay, na.rm = TRUE),
    mean_dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
 ggplot(aes(y=canceled_per_day)) + 
 geom_point(aes(x=mean_arr_delay,colour = "red")) + 
  geom_point(aes(x=mean_dep_delay,colour = "blue"))+
  labs(x = "Average arrive or depart delay flights", y = "The number of canceled flight (no air time")
```


# Flight delays and cancellations appear to have a positive correlation. As the increase in average flight delays, the percentage of canceled flights also rises.